Snow algae 2018 map

### 2020-01-11 manuscript/supp/code/map/drafts/map.Rmd
assembled supplementary materials, moved scripts generating supp figs to manuscript/supp/code

---
title: "Snow algae 2018 map"

---

```{r libs}
library(tidyverse)
library(lubridate)
library(ggmap)
library(ggdark) # ggplot themes
library(googleway) # for getting geographic data from google
library(ggsn) # add symbols to plot
```

```{r data_in}
field <- read_csv(here("data","clean","field_clean.csv"))
```

```{r settings}
key="AIzaSyBJsmyAKTkTg9LT-HdGCCdZdbE2Hjwm-L8"
register_google(key = key) 
theme_set(dark_theme_classic())
```

@@

full_map

ggsave(filename = here::here("figs","map",paste0("full_map.png")),
       plot = full_map, height = 15, width = 20, units = "cm")
```

@@

>>>>

---
title: "Snow algae 2018 map"
---

```{r libs}
library(tidyverse)
library(here)
library(lubridate)
library(ggmap)
library(ggdark) # ggplot themes
library(googleway) # for getting geographic data from google
library(ggsn) # add symbols to plot
```

```{r data_in}
field <- read_csv(here::here("data/02_tidied/tidied_field.csv"))
```

```{r settings}
key="AIzaSyBJsmyAKTkTg9LT-HdGCCdZdbE2Hjwm-L8"
register_google(key = key)
```

@@

full_map
```

@@

ggsave(filename = here::here("figs","map",paste0("full_map.png")),
       plot = full_map, height = 15, width = 20, units = "cm")
